### 2022-11-16 definitions.tex
details

\begin{proposition}
If $S$ is an SWSTS and $I \subseteq S$ is an upward-closed set of states, then $\pred(I )$ is upward-closed.
\end{proposition}
\alain{étrange ces deux propositions}
\iffalse
Proof. Assume $s \in \pred (I )$. Then $s \rightarrow t$ for some $t \in I $. If now $s' \geq s$ then strong upward-compatibility entails that $s' \rightarrow t'$ for some $t' \geq t$. Then $t' \in I$ and $s' \in \pred(I )$.
\fi

@@

(ii) Given a finite set $A \subseteq S$ with $I =\uparrow A$, we can compute a finite basis $B$ of $I$.
\alain{A est déjà une base finie de $\uparrow A$, et $min(A)$ est la base minimale}
\end{fact}

@@

\begin{proof}
We have to show that we can compute a basis of $I^{k+1}$ if we are given a basis of $I^k $. 
Then the
decidability of the stop condition follows directly. Let $B$ be a basis of $I^k$. 
We have
$$I^{k+1} = I \cup pre(I^k ) = I \cup
\bigcup_{s' \in B}
pre(\uparrow \{s' \}).$$
\alain{n'est-ce pas $I^{k+1} = I^k \cup pre(I^k ) = I^k \cup
\bigcup_{s' \in B}
pre(\uparrow \{s' \}).$ ?}
Since $pre(\uparrow \{s' \}$) is computable for any $s'\in S$ by definition, we obtain a finite generating set of $I^{k+1}$ . By
Fact 3, we can compute a basis of $I^{k+1}$.
\end{proof}

\subsection{Defining resilience}

\subsubsection{Resilience}

@@

\problemx{$k$-resilience problem}
{A state $s$ of a TS $(S,\rightarrow)$, two disjoints subset of $S$ $SAFE$ and $BAD$.}
{$\forall s' \in BAD ~ (s \rightarrow^* s') \implies \exists s'' \in SAFE ~ s' \rightarrow^{\leq k} s''$ ?\newline}

@@

We can also ask whether there exists such a bound $k$. We call this problem the bounded resilience problem for TS.

\problemx{Resilience problem}
{A state $s$ of a TS $(S,\rightarrow)$, two disjoints subset of $S$ $SAFE$ and $BAD$.}
{$\exists k \geq 0 ~ \forall s' \in BAD ~ (s \rightarrow^* s') \implies \exists s'' \in SAFE ~ s' \rightarrow^{\leq k} s''$ ?\newline}

\subsubsection{Resilience}

@@

% \textcolor{red}{In the Özkan paper the input include a basis of $\uparrow post^*(s)$. Not $100$\% sure it is necessary, think we can try to do without this assumption in the input.}

>>>>

\begin{proposition}
If $S$ is an SWSTS and $I \subseteq S$ is an upward-closed set of states, then $\pred(I )$ is upward-closed.
\end{proposition}
\alain{étrange ces deux propositions, l'une suffirait}
\iffalse
Proof. Assume $s \in \pred (I )$. Then $s \rightarrow t$ for some $t \in I $. If now $s' \geq s$ then strong upward-compatibility entails that $s' \rightarrow t'$ for some $t' \geq t$. Then $t' \in I$ and $s' \in \pred(I )$.
\fi

@@

(ii) Given a finite set $A \subseteq S$ with $I =\uparrow A$, we can compute a finite basis $B$ of $I$.
\alain{(ii) est bizarre car A est déjà une base finie de $\uparrow A$, et $min(A)$ est la base minimale}
\end{fact}

@@

\begin{proof}
We have to show that we can compute a basis of $I^{k+1}$ if we are given a basis of $I^k $. 
Then the
decidability of the stop condition follows directly. Let $B$ be a basis of $I^k$. 
We have
$$I^{k+1} = I \cup pre(I^k ) = I \cup
\bigcup_{s' \in B}
pre(\uparrow \{s' \}).$$
\alain{n'est-ce pas $I^{k+1} = I^k \cup pre(I^k ) = I^k \cup
\bigcup_{s' \in B}
pre(\uparrow \{s' \}).$ ?}
Since $pre(\uparrow \{s' \}$) is computable for any $s'\in S$ by definition, we obtain a finite generating set of $I^{k+1}$ . By
Fact 3, we can compute a basis of $I^{k+1}$.
\end{proof}
\alain{pas de Fact 3}
\subsection{Defining resilience}

\subsubsection{Resilience for general transition systems}

@@

\problemx{$k$-resilience problem}
{a TS $(S,\rightarrow)$, a state $s \in S$, $SAFE, BAD \subseteq S$ and $SAFE \cap BAD = \emptyset$.}
{$\forall s' \in BAD ~ (s \rightarrow^* s') \implies \exists s'' \in SAFE ~ s' \rightarrow^{\leq k} s''$ ?\newline}

@@

We can also ask whether there exists such a bound $k$. We call this problem the resilience problem.

\problemx{Resilience problem}
{a TS $(S,\rightarrow)$, a state $s \in S$, $SAFE, BAD \subseteq S$ and $SAFE \cap BAD = \emptyset$.}
{$\exists k \geq 0 ~ \forall s' \in BAD ~ (s \rightarrow^* s') \implies \exists s'' \in SAFE ~ s' \rightarrow^{\leq k} s''$ ?\newline}

\subsubsection{Resilience for WSTS}

@@

\alain{dire juste que SAFE = upward closed et BAD = downward closed.
envisager les 3 autres cas. souvent BAD = upward closed (par ex l'exclusion mutuelle).
4 resilience problem (U,D), (U,U), (D,U), (D,D)}
% \textcolor{red}{In the Özkan paper the input include a basis of $\uparrow post^*(s)$. Not $100$\% sure it is necessary, think we can try to do without this assumption in the input.}

### 2022-11-16 proof.tex
details

\begin{lemma}
Let $A \subseteq S$ be a set, $J \subseteq S$ downward-closed and $I \subseteq S$ upward-closed. 
Then $A \cap J \subseteq I \leftrightarrow (\uparrow  A) \cap J \subseteq I$.
\end{lemma}

@@

Procedure 1 enumerates inductive invariants in some fixed order $D_1$ , $D_2$ , . . . , i.e. downward closed subsets $D_i \subseteq S$ such that $\uparrow post(D_i ) \subseteq D_i$. 
Every inductive invariant $D_i$ is an “over-approximation” of $\uparrow post^*(s)$ if it contains $s$.
(on énumère des sur-approximations de la cloture par le haut de $post*(s)$ par leur bases finies).
Each “over-approximation” $D_i$ is given by its basis $b(D_i)$. \textcolor{red}{Notice that, by standard monotonicity, $\uparrow post^*(s)$ is such an inductive invariant and may
eventually be found.}

>>>>

\begin{lemma}
Let $A \subseteq S$, $J \subseteq S$ downward-closed and $I \subseteq S$ upward-closed. 
Then $A \cap J \subseteq I \leftrightarrow (\uparrow  A) \cap J \subseteq I$.
\end{lemma}

@@

Procedure 1 enumerates inductive invariants in some fixed order $D_1$ , $D_2$ , . . . , i.e. downward closed subsets $D_i \subseteq S$ such that $\uparrow post(D_i ) \subseteq D_i$. 
Every inductive invariant $D_i$ is an “over-approximation” of $\uparrow post^*(s)$ if it contains $s$.
(on énumère des sur-approximations de la cloture par le haut de $post*(s)$ par leur bases finies).
Each “over-approximation” $D_i$ is given by its basis $b(D_i)$. \textcolor{red}{Notice that, by standard monotonicity, $\uparrow post^*(s)$ is such an inductive invariant and may
eventually be found.}
\alain{attention D est clos par le bas et $\uparrow post^*(s)$ est clos par le haut, je ne vois pas pourquoi $\uparrow post^*(s) \subseteq D$}
